---
title: "Practice SQL with {sql} Chunks for A6 courseDB.db"
author: "Yong Shi, NEU CS5200 Fall21"
output:
  html_document:
    df_print: paged
---

```{r}
library(RSQLite)

# the path below is a Windows path specification
# on MacOS there is no c:/
fpath = "C:/Users/Yong/Desktop/NN/way home/3s5200/New folder/databases/"
dbfile = "courseDB.db"

dbcon <- dbConnect(RSQLite::SQLite(), paste0(fpath,dbfile))
```



Turn on support for foreign key constraint checking
```{sql connection=dbcon}
PRAGMA foreign_keys = ON
```



/* 1. (5 pts) What are the last names, city, and state of all customer who made at least one purchase? */
```{sql connection=dbcon}
select c.LastName, c.City, c.State, count(inv.CustomerId) as purTimes
from customers c
left join invoices inv on c.CustomerId = inv.CustomerId
where (select count(CustomerId) from invoices group by CustomerId) > 0
group by c.CustomerId
```



/* 2. (5 pts) What are the titles of each albums and the artists who created it? */
```{sql connection=dbcon}
select a.AlbumId, a.Title, at.Name as artistName
from albums a 
join artists at on a.ArtistId = at.ArtistId
```



/* 3. (10 pts) What are the total number of unique customers for each country, ordered alphabetically by country who made at least one purchase? */
```{sql connection=dbcon}
CREATE VIEW purTimes as
select CustomerId, count(CustomerId) as totalNum
from invoices
group by CustomerId
HAVING totalNum > 0
```

```{sql connection=dbcon}
select c.Country, count(c.CustomerId) as totalNum
from customers c
join purTimes p on c.CustomerId = p.CustomerId
group by c.Country
ORDER BY c.Country ASC
```



/* 4. (10 pts) How many customers never made a purchase, i.e., they appear in the customers table but not in the invoices table. */
```{sql connection=dbcon}
select count(*) from (select distinct c.LastName, c.CustomerId, inv.CustomerId
from customers c
left join invoices inv on c.CustomerId = inv.CustomerId
where inv.InvoiceId is null)
```



/* 5. What are the names of the albums containing the substring "symphony" in the album title? */
```{sql connection=dbcon}
select AlbumId, Title
from albums 
where Title like '%symphony%'
```



/* 6. What are the names of all artists who performed MPEG (video or audio) tracks in either the "Brazilian Music" or the "Grunge" playlists? */
```{sql connection=dbcon}
select distinct ar.Name, ar.ArtistId, pl.Name, me.Name as meName
from artists ar
join albums al on ar.ArtistId = al.ArtistId
join tracks tr on al.AlbumId = tr.AlbumId
join playlist_track plt on tr.TrackId = plt.TrackId
join playlists pl on plt.PlaylistId = pl.PlaylistId
join media_types me on tr.MediaTypeId = me.MediaTypeId
where pl.Name in ('Brazilian Music', 'Grunge') and me.Name like '%MPEG%'
```



/* 7. How many artists published at least 3 MPEG audio tracks? */
```{sql connection=dbcon}
create VIEW artMPEGautio as
select ar.Name, ar.ArtistId, al.AlbumId, tr.MediaTypeId, me.Name as MPEGName
from artists ar
join albums al on ar.ArtistId = al.ArtistId
join tracks tr on al.AlbumId = tr.AlbumId
join media_types me on tr.MediaTypeId = me.MediaTypeId
where me.Name = 'MPEG audio file'
```

```{sql connection=dbcon}
select count(*)
from (select Name, ArtistId, MPEGName, count(MPEGName) as cnt
from artMPEGautio
group by Name
HAVING cnt > 2)
```



/* 8. What is the total amount of music for each genre (in hours)? List the genre and time rounded to two decimals. */
```{sql connection=dbcon}
select tr.GenreId, ge.Name, sum(tr.Milliseconds), round(sum(cast(tr.Milliseconds as float))/1000/60/60, 2) as sumHrs
from tracks tr
join genres ge on tr.GenreId = ge.GenreId
group by tr.GenreId
```



```{r}
dbDisconnect(dbcon)
```





/* below are my helper queries */
```{sql connection=dbcon}
drop view artMPEGautio
```

```{sql connection=dbcon}
select * from artMPEGautio
```

```{sql connection=dbcon}
CREATE TEMPORARY TABLE sumBonus AS
select WORKER_REF_ID, sum(BONUS_AMOUNT) as sumBs from Bonus group by WORKER_REF_ID
```
```{sql connection=dbcon}
select * from sumBonus
```
```{sql connection=dbcon}
DROP TABLE sumBonus
```

```{sql connection=dbcon, output.var="customers.df"}
select * from customers
```

```{sql connection=dbcon, output.var="invoices.df"}
select * from invoices
```


```{sql connection=dbcon}
select * from tracks
```

```{sql connection=dbcon}
select CustomerId, count(CustomerId)
from invoices
group by CustomerId
```

```{sql connection=dbcon}
select * from Title
```



















```{r}
dbListTables(dbcon)
dbListFields(dbcon, "Students")
dbListFields(dbcon, "Courses")
```


```{sql connection=dbcon}
DROP TABLE IF EXISTS Students
```

```{sql connection=dbcon}
CREATE TABLE Students(
  sid INTEGER NOT NULL,
  sname TEXT NOT NULL,
  major TEXT NOT NULL,
  gpa float NOT NULL,
  PRIMARY KEY (sid)
)
```

```{sql connection=dbcon}
SELECT * FROM Students;
```

```{sql connection=dbcon}
DROP TABLE IF EXISTS College
```

```{sql connection=dbcon}
CREATE TABLE College(
  cid TEXT NOT NULL,
  cname TEXT NOT NULL,
  PRIMARY KEY (cid)
)
```

```{sql connection=dbcon}
SELECT * FROM College;
```


```{sql connection=dbcon}
DROP TABLE IF EXISTS Enrollment
```

```{sql connection=dbcon}
CREATE TABLE Enrollment(
  sid INTEGER NOT NULL,
  cid TEXT NOT NULL,
  grade INTEGER NOT NULL,
  onCoop TEXT NOT NULL,
  --PRIMARY KEY (sid),
  FOREIGN KEY (sid) REFERENCES Students(sid),
  FOREIGN KEY (cid) REFERENCES College(cid)
)
```

```{sql connection=dbcon}
SELECT * FROM Enrollment;
```


```{sql connection=dbcon}
INSERT INTO Students VALUES 
  (3,"alex","Philosophy", 3.6),
  (2,"baby","Philosophy",3.9),
  (1,"cow","English",3.9),
  (4,"dog","Economics",3.5),
  (5,"egg","Math",3.9)
```

```{sql connection=dbcon}
INSERT INTO Enrollment VALUES 
  (3,"91.573",50,"Y"),
  (2,"14.601",40,"Y"),
  (1,"91.573",50,"N"),
  (4,"14.601",40,"N"),
  (5,"91.573",50,"N")
```


```{sql connection=dbcon}
INSERT INTO College VALUES 
  ("91.573","Khoury"),
  ("14.601","Y"),
  ("5600","N")
```

```{sql connection=dbcon}
select sid, count(cid) from Enrollment 
group by sid having count(cid) > 2
```

```{sql connection=dbcon}
SELECT s.sname FROM Students s
JOIN (select sid, count(cid) from Enrollment group by sid having count(cid) > 2) e ON s.sid = e.sid
WHERE s.major = 'Philosophy'
```


```{sql connection=dbcon}
SELECT sid, cid, grade FROM Enrollment WHERE cid in ('91.573','14.601') AND grade < 60
```

```{sql connection=dbcon}
SELECT DISTINCT s.sname FROM Students s
JOIN (SELECT sid, cid, grade FROM Enrollment WHERE cid in ('91.573','14.601') AND grade < 60) e ON s.sid = e.sid
WHERE s.major in ('Economics', 'Math')
```


```{sql connection=dbcon}
SELECT cid, cname FROM College WHERE cname = 'Khoury'
```

```{sql connection=dbcon}
SELECT count(*) FROM(
SELECT e.sid, e.cid, e.onCoop FROM Enrollment e 
JOIN (SELECT cid, cname FROM College WHERE cname = 'Khoury') c ON e.cid = c.cid
JOIN (SELECT sid, gpa FROM Students WHERE gpa > 3.8) s ON e.sid = s.sid
WHERE onCoop = 'N'
)
```







