---
title: "Yong Shi A5 CS5200 Fall21.Rmd"
output:
  html_document:
    df_print: paged
---

```{r}
library(RSQLite)

fpath = "C:/Users/Yong/Desktop/NN/way home/3s5200/New folder/databases/"
dbfile = "courseA3DB.sqlite"

dbcon <- dbConnect(RSQLite::SQLite(), paste0(fpath,dbfile))
```

```{sql connection=dbcon}
DROP TABLE IF EXISTS Course
```

```{sql connection=dbcon}
CREATE TABLE Course(
  number TEXT NOT NULL,
  title TEXT NOT NULL,
  lengthInDays INTEGER NOT NULL,
  PRIMARY KEY (number)
)
```

```{sql connection=dbcon}
SELECT * FROM Course;
```


```{sql connection=dbcon}
DROP TABLE IF EXISTS Lesson
```


```{sql connection=dbcon}
CREATE TABLE Lesson(
  tid INTEGER NOT NULL,
  title TEXT NOT NULL,
  lengthInHrs INTEGER NOT NULL,
  subject INTEGER NOT NULL,
  PreReqLessonId INTEGER NOT NULL,
  PRIMARY KEY (tid),
  FOREIGN KEY (PreReqLessonId) REFERENCES PreLesson(PreReqLessonId),
  FOREIGN KEY (subject) REFERENCES SubjectList(subject) ON DELETE RESTRICT
)
```


```{sql connection=dbcon}
SELECT * FROM Lesson;
```


/* I put a  TRIGGER to control each course duration within 3hrs, the lengthInHrs if is
over 3 hrs when insert, will about and throw warning 'Invalid length, need within 3hrs'.
This is because there is limited classrooms, so the course should be finished on time,
to give room to next course. Also if one course is too long, that will not get a good
concentration from students. So I think this is a reasonable TRIGGER. */

```{sql connection=dbcon}
CREATE TRIGGER validate
BEFORE INSERT ON Lesson
BEGIN
SELECT
CASE
WHEN NEW.lengthInHrs > 3
THEN RAISE (ABORT,'Invalid length, need within 3hrs')
END;
END;
```


```{sql connection=dbcon}
INSERT INTO Lesson VALUES 
  (5,"5004",4,3,0)
```


```{sql connection=dbcon}
DROP TABLE IF EXISTS SubjectList
```

```{sql connection=dbcon}
CREATE TABLE SubjectList(
  subject INTEGER NOT NULL,
  list TEXT NOT NULL,
  PRIMARY KEY (subject)
)
```

```{sql connection=dbcon}
SELECT * FROM SubjectList;
```


```{sql connection=dbcon}
DROP TABLE IF EXISTS PreLesson
```

```{sql connection=dbcon}
CREATE TABLE PreLesson(
  PreReqLessonId INTEGER NOT NULL,
  tid INTEGER NOT NULL,
  PRIMARY KEY (PreReqLessonId),
  FOREIGN KEY (tid) REFERENCES Lesson(tid) ON DELETE RESTRICT ON UPDATE CASCADE
)
```

```{sql connection=dbcon}
SELECT * FROM PreLesson;
```


```{sql connection=dbcon}
DROP TABLE IF EXISTS Unit
```

```{sql connection=dbcon}
CREATE TABLE Unit (
  number TEXT NOT NULL,
  tid INTEGER NOT NULL,
  PRIMARY KEY (number),
  FOREIGN KEY (number) REFERENCES Course(number),
  FOREIGN KEY (tid) REFERENCES Lesson(tid)
)
```

```{sql connection=dbcon}
SELECT * FROM Unit;
```


```{sql connection=dbcon}
INSERT INTO Course (number,title,lengthInDays) VALUES 
  ("100","CS",28),
  ("200","ME",56),
  ("300","IE",28),
  ("400","QE",28);
```


```{sql connection=dbcon}
INSERT INTO Lesson VALUES 
  (3,"5200",2,1,1),
  (2,"5008",3,2,1),
  (1,"5001",3,3,0),
  (4,"5002",2,3,0)
```


```{sql connection=dbcon}
INSERT INTO PreLesson VALUES 
  (3,1),
  (2,1),
  (1,0)
```


```{sql connection=dbcon}
INSERT INTO SubjectList VALUES 
  (1,"ML"),
  (2,"SQL"),
  (3,"R"),
  (4,"java")
```


```{sql connection=dbcon}
INSERT INTO Unit VALUES 
  ("200",2),
  ("300",3),
  ("100",1)
```


```{sql connection=dbcon}
PRAGMA foreign_keys = ON
```


```{r}
dbListTables(dbcon)
dbListFields(dbcon, "Course")
dbListFields(dbcon, "Lesson")
dbListFields(dbcon, "PreLesson")
dbListFields(dbcon, "SubjectList")
dbListFields(dbcon, "Unit")
```

```{r}
dbDisconnect(dbcon)
```

